Chum Populations

### 2015-07-06 paper/main.tex
genome scan notebook and work

 - inference of adaptation - life history variation  - Fst across the genome.

@@

\section*{Introduction}
To do

Expected population structure

ESA listing - summer chum ESU

Salmonid WGD

@@

@@

Map construction follows Waples (2015)

@@

Genotyping duplicate loci using the dominance coding suggested by Patterson (2006). 
Individual-based analyses
\begin{itemize}
	\item PCAs - How do compare? - maybe measure info loss?
    \item Heterozygosity
	\item Fst across the genome
\end{itemize}

Population-based analyses
\begin{itemize}
	\item MAF, Heterozygosity
	\item Fst across the genome
    \item Effective population size - Waples and Do
    \item Bayescan outlier tests
\end{itemize}

@@

@@

congruence of paralog across families (supplemental table)

@@

\includegraphics[scale=.3]{figures/PCA_dom_paralogs.png}
\includegraphics[scale=.3]{figures/PCA_codom_subsample.png}
\subsection*{Population Genetics}

measure information loss from dominance coding
discuss population vs individual based results
paralogs have similar neutral patterns of population structure.
can we demonstrate contained within paralogs by bootstrapping 
Genome scans (Outliers) - LG regions highlighted.

@@

\section*{Supplemental}

\begin{figure}[H]
\includegraphics[scale=.3]{figures/supplemental/ascertainment.png}
\caption{Minor allele frequency distribution for all genotyped loci (blue) and just the loci placed on the linkage map (green). The increase in MAF shows the effect of ascertainment bias.}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[scale=.4]{figures/supplemental/synteny_chinook.png}
\caption{Oxford grid - Chum and Chinook linkag groups.}
\end{figure}

>>>>

@@

\section*{Introduction}

\begin{itemize}

\item PS chum pop gen
\begin{itemize}
\item Population structure
\item life history variation
\item ESA listing - summer chum ESU
\item Effective population size
\end{itemize}

\item Genome scan
\begin{itemize}
\item paired population design
\item map-assisted
\item draw on synteny / orthology
\end{itemize}

\item Genotyping duplicates
\begin{itemize}
\item Legacy of the salmonid WGD
\item uncharacterized regions of the genome
\item first approach in salmon using next-gen seq data.  Method applicable to other species with WGD?

\end{itemize}

\item Map
\begin{itemize}
\item consensus map w/centromeres
\item synteny
\item annotation
\end{itemize}

\end{itemize}

@@

Genotyping duplicate loci using the dominance coding suggested by Patterson (2006). 
Individual-based analyses
\begin{itemize}
    \item PCAs - How do these two methods compare? - maybe measure info loss?
    \item Formal tests for population structure - tracey-widom stats

\end{itemize}

Population-based analyses
\begin{itemize}
	\item MAF, Heterozygosity
    \item phylogenetic tree
	\item Fst across the genome
    \item Effective population size -

    	Effective population size was estimated for each population using the LD method implemented in the LDNe software package (Waples and Do).  The LD methods estimates average  correlation of alleles at pairs of loci (r2). The mean pairwise r2 value across unlinked loci provides an estimate of contemporary effective population size (WAPLES). The linkage map was used to ensure that only pairs of loci not co-located on a chromosome were used to calculate mean r2. 
    \item Bayescan outlier tests
\end{itemize}

@@

Map construction follows McKinney (2015), based off Waples (2015)

@@

@@

\includegraphics[scale=.3]{figures/PCA_dom_paralogs.png}
\includegraphics[scale=.3]{figures/PCA_codom_subsample.png}
paralogs have similar neutral patterns of population structure.
measure information loss from dominance coding

discuss population vs individual based results

can we demonstrate contained within paralogs by bootstrapping 
Genome scans - LG regions highlighted.

@@

congruence of identified homeologs across families (supplemental table)

@@

@@

Coalescent!

 - inference of adaptation -associated  life history variation  - Fst across the genome.

\pagebreak
\section*{Supplemental}

\begin{figure}[H]
\includegraphics[scale=.3]{figures/supplemental/ascertainment.png}
\caption{Minor allele frequency (MAF) distribution for all genotyped loci (blue) and just the loci placed on the linkage map (green). The rightward shift in the MAF distributino shows the effect of ascertainment bias within the mapped loci.}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[scale=.25]{figures/supplemental/synteny_chinook.png}
\caption{Oxford grid - Chum and Chinook linkage groups.  Loci are positioned according to the order within each genome.}
\end{figure}
